Initial Analysis

### 2019-12-31 Initial_Analysis.Rmd
Changed plots colors

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "data.table", # Read dataframe (Fast!)
  "wesanderson",
  "tidyverse", # for all data wrangling and ggplot
  "janitor", # for data cleaning
  "tidytext", # to order the facet wrap https://juliasilge.com/blog/reorder-within/
  "cowplot", # for figures 1 and 3
  # "ggimage", #for reading images to the circular plot
  # "ggrepel", # for nice plot labels
  # "ggsflabel", # for nice sf_plots labels
  "spdep", # for poly2nb
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  # "purrr",#Spatial analysis
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "parallel", # for parallelization
  # "taxize", # For getting species names
  "rfishbase", # for species ecosystem affinity
  "zoo" #for runing mean
)

@@

Revenue_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  full_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Revenue_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity) %>% # Estimate the amount of dollars of each nation 
  summarise(Total_USD = (sum(mean_value,na.rm=T))/1000000) %>% # Million of USD
  ungroup() %>% 
  mutate(#fishing_entity = ifelse(fishing_entity == "USA","United States of America",
                                 # ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)
                                 # ),
         Bins = cut(Total_USD,breaks = Rev_Breaks, dig.lab = 5 ),
         Bins_Plot = cut(Total_USD,breaks = Rev_Breaks,
                         labels = c('super low', 'low','median','high','super high'),
                         dig.lab = 5 # Removes scientific notaion
                         )
  ) %>% 
  filter(Total_USD > 0)

@@

@@

ggsave(
    plot = last_plot(),
    width = 17,
    height = 15,
    units = "in",
    filename = "Territory_circular_status.png",
    path = Figures_Path
  )

@@

Species_Data <- Tresholded_T_Data %>% 
  group_by(taxon_key) %>% 
  summarise(n_trans_spp = length(unique(fishing_entity))) %>% 
  left_join(Exploited_Species) %>%
  rename(scientific_name = taxon_name) %>% 
  left_join(Species_environ_list) %>%
  mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",
                              ifelse(DemersPelag %in% c("bathypelagic","benthopelagic"), "bathy-bento-pelagic",paste(DemersPelag)
                                     )
                              ),
         n_trans_spp = ifelse(n_trans_spp > 100, 100, n_trans_spp),
         DemersPelag = str_to_title(DemersPelag)
         ) %>% 
  select(individual=scientific_name,
         value = n_trans_spp,
         group = DemersPelag) %>% 
  arrange(group,value)  %>% 
  mutate(
    individual = ifelse(individual == "Chloroscombrus chrysurus", "C. chrysurus",
                        ifelse(individual == "Scomberomorus commerson", "S. commerson",
                               individual)
    )
  )

@@

  # If you want to show catch  
Country_Spp_Data <- Tresholded_T_Data %>%
  left_join(Exploited_Species) %>%
  left_join(Top_5_Ecosystem) %>% # includes the groups
  filter(taxon_name %in% Top_5_Ecosystem$taxon_name) %>%
  # mutate(taxon_key = as.character(taxon_key)) %>%
  left_join(SAU_Catch_Data,
            by = c("eez_name","taxon_key")
  ) %>%
  group_by(fishing_entity,group) %>%
  summarise(top_catch = sum(total_catch)) %>%
  group_by(group) %>%
  top_n(5) %>% 
  mutate(
    fishing_entity = ifelse(fishing_entity == "Korea (South)", "S. Korea",
                            ifelse(fishing_entity == "Russian Federation","Russia",
                                   ifelse(fishing_entity == "Papua New Guinea", "N.Guinea",
                                          ifelse(fishing_entity == "Solomon Isl.", "Solomon",fishing_entity)))
    )
  )
```

@@

                    values = c(wes_palette(n = 4, name = "GrandBudapest1"),
                               wes_palette(n = 3, name = "GrandBudapest2")

@@

Ecosystem_plots <- Country_Spp_Data %>%
  ungroup() %>% 
  mutate(name = reorder_within(fishing_entity,top_catch,group)) %>% # to order the facet wrap
  ggplot() +
  geom_bar(
    aes(
      x = name,
      y = top_catch/1000,
      fill = group
    ), 
    stat = "identity"
  ) +
  labs(x = "",
       y = "Catch (Thousand tonnes)") +
  scale_fill_manual("",
                    values = c(wes_palette(n = 4, name = "GrandBudapest1"),
                               wes_palette(n = 3, name = "GrandBudapest2")
                    ),
                    na.value = "white"
  ) +
  facet_wrap(~group,
             nrow=2,
             scales = "free") +
  ggtheme_plot() +
  scale_x_reordered() +
  theme(legend.position = "",
        axis.text.x = element_text(size = 11,
                               angle = 0,
                               face = "plain"),
          strip.background = element_blank(),
  strip.text.x = element_blank()
  )

@@

Area_Index_Level <- seq(.1,0.5,0.1)

@@

  data <- Clean_Results_Trans %>% 
    filter(
      Area_Index >= Area_Index_Level[i],
      Area_Index <= 1-Area_Index_Level[i],
      Model_Index == MI
    ) %>% 
    group_by(Territory) %>% 
    summarise(
      n_trans_spp = length(unique(TaxonKey)),
      n_Neighbours = length(unique(Neighbour)),
      Trans_Rate = n_trans_spp/n_Neighbours
    )

@@

  p[[i]] <- ggplot(data) +
    geom_histogram(aes(n_trans_spp),
                   binwidth = 10, 
                   colour = "white"
    ) +
    labs(
      x = "Transboundary species (n)",
      y = "Frequency of EEZs",
      title= paste("Using a",(Area_Index_Level[i]*100),"% area treshold. (Median",Median_data,")")
    ) +
    # ggtitle(paste("Using a",(Area_Index_Level[i]*100),"% area treshold. (Median",Median_data,")")) +
    ggtheme_plot()

>>>>

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "data.table", # Read dataframe (Fast!)
  "wesanderson",
  "tidyverse", # for all data wrangling and ggplot
  "janitor", # for data cleaning
  "tidytext", # to order the facet wrap https://juliasilge.com/blog/reorder-within/
  "cowplot", # for figures 1 and 3
  # "ggimage", #for reading images to the circular plot
  # "ggrepel", # for nice plot labels
  # "ggsflabel", # for nice sf_plots labels
  # "spdep", # for poly2nb old
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  # "purrr",#Spatial analysis
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "parallel", # for parallelization
  # "taxize", # For getting species names
  "rfishbase", # for species ecosystem affinity
  "zoo" #for runing mean
)

@@

Revenue_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  full_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Revenue_Data,
            by = c("fishing_entity","fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity) %>% # Estimate the amount of dollars of each nation 
  summarise(Total_USD = (sum(mean_value,na.rm=T))/1000000) %>% # Million of USD
  ungroup() %>% 
  mutate(#fishing_entity = ifelse(fishing_entity == "USA","United States of America",
                                 # ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)
                                 # ),
         Bins = cut(Total_USD,breaks = Rev_Breaks, dig.lab = 5 ),
         Bins_Plot = cut(Total_USD,breaks = Rev_Breaks,
                         labels = c('super low', 'low','median','high','super high'),
                         dig.lab = 5 # Removes scientific notaion
                         )
  ) %>% 
  filter(Total_USD > 0)

@@

Catch_Breaks <- c(-1,10,100,1000,5000,10000)

@@

ggsave(
    plot = last_plot(),
    width = 17,
    height = 15,
    units = "in",
    filename = "Plot.png"
    # filename = "Territory_circular_status.png",
    # path = Figures_Path
  )

@@

Species_Data <- Tresholded_T_Data %>% 
  group_by(taxon_key) %>% 
  summarise(n_trans_spp = length(unique(fishing_entity))) %>% 
  left_join(Exploited_Species) %>%
  rename(scientific_name = taxon_name) %>% 
  left_join(Species_environ_list) %>%
  mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",
                              ifelse(DemersPelag %in% c("bathypelagic","benthopelagic"), "bathy-bento-pelagic",paste(DemersPelag)
                                     )
                              ),
         n_trans_spp = ifelse(n_trans_spp > 100, 100, n_trans_spp),
         DemersPelag = str_to_title(DemersPelag)
         ) %>% 
  select(individual=scientific_name,
         value = n_trans_spp,
         group = DemersPelag) %>% 
  arrange(group,value)  %>% 
  mutate(
    individual = ifelse(individual == "Chloroscombrus chrysurus", "C. chrysurus",
                        ifelse(individual == "Scomberomorus commerson", "S. commerson",
                               individual)
    )
  ) %>% 
  filter(!group %in% c("Bathydemersal","Pelagic"))

@@

  # If you want to show catch  
Country_Spp_Data <- Tresholded_T_Data %>%
  left_join(Exploited_Species) %>%
  left_join(Top_5_Ecosystem) %>% # includes the groups
  filter(taxon_name %in% Top_5_Ecosystem$taxon_name) %>%
  left_join(SAU_Catch_Data,
            by = c("eez_name","taxon_key")
  ) %>%
  group_by(fishing_entity,group) %>%
  summarise(top_catch = sum(total_catch)) %>%
  group_by(group) %>%
  top_n(5) %>% 
  mutate(
    fishing_entity = ifelse(fishing_entity == "Korea (South)", "S. Korea",
                            ifelse(fishing_entity == "Russian Federation","Russia",
                                   ifelse(fishing_entity == "Papua New Guinea", "N.Guinea",
                                          ifelse(fishing_entity == "Solomon Isl.", "Solomon",fishing_entity)))
    )
  )

@@

                               wes_palette(n = 3, name = "Darjeeling2")

@@

Ecosystem_plots <- Country_Spp_Data %>%
  ungroup() %>% 
  mutate(name = reorder_within(fishing_entity,top_catch,group)) %>% # to order the facet wrap
  ggplot() +
  geom_bar(
    aes(
      x = name,
      y = top_catch/1000,
      fill = group
    ), 
    stat = "identity"
  ) +
  labs(x = "",
       y = "Catch (Thousand tonnes)") +
  scale_fill_manual("",
                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
                               wes_palette(n = 3, name = "Darjeeling2")
                    ),
                    na.value = "white"
  ) +
  facet_wrap(~group,
             nrow=2,
             scales = "free") +
  ggtheme_plot() +
  scale_x_reordered() +
  theme(legend.position = "",
        axis.text.x = element_text(size = 11,
                               angle = 0,
                               face = "plain"),
          strip.background = element_blank(),
  strip.text.x = element_blank()
  )

@@

Area_Index_Level <- c(seq(.1,0.5,0.1),0.25)
result <- c(40,35,28,18,4,31.5)

plot(result~Area_Index_Level)

@@

  data <- Clean_Results_Trans %>% 
    filter(
      area_index >= Area_Index_Level[i],
      area_index <= 1-Area_Index_Level[i],
      model_index == MI
    ) %>% 
    group_by(eez_name) %>% 
    summarise(
      n_trans_spp = length(unique(taxon_key)),
      n_Neighbours = length(unique(eez_neighbour)),
      Trans_Rate = n_trans_spp/n_Neighbours
    )

@@

  p[[i]] <- ggplot(data) +
    geom_histogram(aes(n_trans_spp),
                   binwidth = 10, 
                   colour = "white",
                   fill = ifelse(i!= 6,"grey80","grey20")
    ) +
    labs(
      x = "Transboundary species (n)",
      y = "Frequency of EEZs",
      title= paste((Area_Index_Level[i]*100),"% area treshold"," (Median ",Median_data,")",sep="")
    ) +
    # ggtitle(paste("Using a",(Area_Index_Level[i]*100),"% area treshold. (Median",Median_data,")")) +
    ggtheme_plot()
}
